UniScatter: Unifying\\Backscatter Communications, Symbiotic Radio and Reconfigurable Intelligent Surface

### 2022-08-08 main.tex
:pencil: Update introduction

% dark mode
\usepackage{xcolor} \pagecolor[rgb]{0,0,0} \color[rgb]{1,1,1}

@@

% glossaries-extra
\setabbreviationstyle[acronym]{long-short}
\newacronym{af}{AF}{Amplify-and-Forward}
\newacronym{ambc}{AmBC}{Ambient Backscatter Communications}
\newacronym{ap}{AP}{Access Point}
\newacronym{awgn}{AWGN}{Additive White Gaussian Noise}
\newacronym{bcd}{BCD}{Block Coordinate Descent}
\newacronym{bc}{BackCom}{Backscatter Communications}
\newacronym{bibo}{BIBO}{Binary-Input Binary-Output}
\newacronym{bpcu}{\si{bpcu}}{bits per channel use}
\newacronym{bpsphz}{\si{bps/Hz}}{bits per second per Hertz}
\newacronym{cp}{CP}{Canonical Polyadic}
\newacronym{cr}{CR}{Cognitive Radio}
\newacronym{cscg}{CSCG}{Circularly Symmetric Complex Gaussian}
\newacronym{csi}{CSI}{Channel State Information}
\newacronym{df}{DF}{Decode-and-Forward}
\newacronym{dmc}{DMC}{Discrete Memoryless Channel}
\newacronym{dmtc}{DMTC}{Discrete Memoryless Thresholding Channel}
\newacronym{dmtmac}{DMTMAC}{Discrete Memoryless Thresholding Multiple Access Channel}
\newacronym{dtmac}{DTMAC}{Discrete Thresholding Multiple Access Channel}
\newacronym{dp}{DP}{Dynamic Programming}
\newacronym{fdma}{FDMA}{Frequency-Division Multiple Access}
\newacronym{iid}{i.i.d.}{independent and identically distributed}
\newacronym{ioe}{IoE}{Internet of Everything}
\newacronym{iot}{IoT}{Internet of Things}
\newacronym{kkt}{KKT}{Karush-Kuhn-Tucker}
\newacronym{m2m}{M2M}{Machine to Machine}
\newacronym{mac}{MAC}{Multiple Access Channel}
\newacronym{mc}{MC}{Multiplication Coding}
\newacronym{miso}{MISO}{Multiple-Input Single-Output}
\newacronym{mimo}{MIMO}{Multiple-Input Multiple-Output}
\newacronym{ml}{ML}{Maximum-Likelihood}
\newacronym{noma}{NOMA}{Non-Orthogonal Multiple Access}
\newacronym{ofdm}{OFDM}{Orthogonal Frequency-Division Multiplexing}
\newacronym{pdf}{PDF}{Probability Density Function}
\newacronym{pgd}{PGD}{Projected Gradient Descent}
\newacronym{psk}{PSK}{Phase Shift Keying}
\newacronym{qam}{QAM}{Quadrature Amplitude Modulation}
\newacronym{qos}{QoS}{Quality of Service}
\newacronym{rf}{RF}{Radio-Frequency}
\newacronym{rfid}{RFID}{Radio-Frequency Identification}
\newacronym{ris}{RIS}{Reconfigurable Intelligent Surface}
\newacronym{sc}{SC}{Superposition Coding}
\newacronym{sic}{SIC}{Successive Interference Cancellation}
\newacronym{simo}{SIMO}{Single-Input Multiple-Output}
\newacronym{sinr}{SINR}{Signal-to-Interference-plus-Noise Ratio}
\newacronym{smawk}{SMAWK}{Shor-Moran-Aggarwal-Wilber-Klawe}
\newacronym{snr}{SNR}{Signal-to-Noise Ratio}
\newacronym{sr}{SR}{Symbiotic Radio}
\newacronym{tdma}{TDMA}{Time-Division Multiple Access}
\newacronym{ue}{UE}{user}
\newacronym{wit}{WIT}{Wireless Information Transfer}
\newacronym{wpcn}{WPCN}{Wireless Powered Communication Network}
\newacronym{wpt}{WPT}{Wireless Power Transfer}

\begin{document}
\title{UniScatter: Unifying\\Backscatter Communications, Symbiotic Radio, and Reconfigurable Intelligent Surface}
\author{
	\IEEEauthorblockN{
		Yang~Zhao,~\IEEEmembership{Member,~IEEE,}
		and~Bruno~Clerckx,~\IEEEmembership{Fellow,~IEEE}
	}
	\thanks{
		The authors are with the Department of Electrical and Electronic Engineering, Imperial College London, London SW7 2AZ, U.K. (e-mail: \{yang.zhao18, b.clerckx\}@imperial.ac.uk).
	}
}
\maketitle

\begin{abstract}
	Scatterers can harvest energy from, modulate information over, and influence propagation of surrounding radio waves.
	\gls{bc} varies object impedance to manipulate the magnitude, phase, and/or frequency of scattered signal to encode information and deliver within coverage.
	\gls{ris} adapts scattering antennas or programmable metamaterial to control wireless propagation environment by boosting/suppressing signal strength in specific directions.
	\gls{sr} incorporates scatter nodes into active networks that recycle ambient signal to transmit self information and enhance legacy channel to the cooperative receiver.
	In this paper, we depart from those concepts and introduce UniScatter as a new paradigm for future wireless networks.
	Instead of treating probability distribution of reflection states as equiprobable (as scattering source of \gls{bc}/\gls{sr}) or degenerate (as reflecting element of \gls{ris}), UniScatter node adapts the input distribution of a passive scatterer based on link priority and \gls{csi}, balancing information encoding and channel reconfiguration in a flexible and mutualistic manner.
	To accommodate signal characteristics, UniScatter receiver semi-coherently decodes all nodes from accumulated energy, determines equivalent primary channel over reflection pattern, then coherently decodes the primary link under enhanced multipath.
	It reduces the complexity of cooperative decoding while preserves the benefits of backscatter modulation and passive beamforming.
	Using shared spectrum, energy, and infrastructures, UniScatter is a general and powerful transmit-assist protocol that unifies \gls{bc}, \gls{ris} and \gls{sr} with universal hardware design and augmented \gls{qos} control.
	We consider an application scenario where a multi-antenna \gls{ap} serves a single-antenna user surrounded by multiple UniScatter nodes, and characterize the achievable primary-(total-)backscatter rate region by designing input distribution at the nodes, active beamforming at the \gls{ap}, and backscatter decision design at the user.
	Simulation results demonstrate UniScatter nodes can flexibly control the transmit-assist tradeoff via smart input distribution design.
\end{abstract}

@@

	To the best of our knowledge, all relevant literatures assumed either Gaussian codebook \cite{Guo2019b,Ding2020,Long2020a,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Hu2021b} or finite equiprobable inputs \cite{Yang2018,Liang2020,Han2021,Zhang2022,Liu2019d,Bereyhi2020,Xu2020b,Zhang2021d,Hua2022,Basar2020,Ma2020a,Yuan2021,Hu2021a} at backscatter information sources.
	The former is impractical for passive backscatter devices, while the latter does not fully exploit reflection pattern and \gls{csi}.
	In this paper, we introduce the concept of UniScatter that generalizes \gls{bc}, \gls{sr}, and \gls{ris} to manipulate the transmit-assist tradeoff via smart input distribution and backscatter detector design.
	The contributions of this paper are summarized as follows.

	\emph{First,} we propose the UniScatter node that adapt input probability distribution of a finite-state passive scatter device based on link priority and \gls{csi}.
	The reflection pattern over time is no longer fully random or deterministic, but can be flexibly distributed to unify and balance backscatter modulation and passive beamforming.
	Scattering source of \gls{bc}/\gls{sr} and reflecting element of \gls{ris} can be regarded as its extreme cases, where the input distirbution boils down to equiprobable and degenerate, respectively.
	Like aforementioned \gls{ris}-empowered \gls{bc}/\gls{sr} schemes, it requires regular coordination with passive nodes, but the advantages are 1) UniScatter nodes can be built over conventional load-switching scatterers instead of metamaterial; 2) the optimization cost of input distribution is much lower than that of \gls{ris} reflection coefficients; 3) adaptive backscatter channel coding can achieve higher instantaneous backscatter rate.

	\emph{Second,} we propose a novel backscatter re

	To fully accommodate backscatter characteristics, we also propose a novel receiving strategy that first jointly decodes all Metascatter from accumulated energy, then models their reflection pattern and backscatter paths within equivalent channel for primary decoding.
	Since backscatter message is modulated over primary signal, backscatter decoding is indeed part of primary channel training, and there is no need for operation-intensive \gls{sic} at the receiver.

	The reflection pattern over time is no longer fully random or deterministic, but can be flexibly distributed to balance backscatter encoding and passive beamforming.
	For single-user scenario, when primary link is absolutely prioritized, the distribution falls on one state and Metascatter boils down to conventional \gls{ris}.
	When only considering backscatter performance, the distribution involves the highest entropy and Metascatter is essentially an \gls{ambc} node.

	nodes that adapts the input probability distribution of a finite-state passive backscatter device based on primary and (cascaded) backscatter \gls{csi} to unify and generalize parasitic source of \gls{sr} and reflecting elements of \gls{ris}.

	% Motivated by those, we propose the concept of Metascatter, which adapts the input distribution of a passive backscatter node to generalize backscatter sources of \gls{sr} and reflecting elements of \gls{ris}.
	% An application scenario was considered where multiple Metascatters are introduced to conventional point-to-point system and adapt their input probability distribution to simultaneously act as backscatter tags of \gls{sr} and reflecting elements of \gls{ris}.
	% An application scenario was considered where multiple Metascatters ride over a point-to-point transmission and simultaneously perform backscatter encoding and passive beamforming.
	% Compared to existing \gls{ris}-empowered \gls{sr} that encodes and precodes independently using advanced architecture (e.g., overlay or parallel), Metascatter softly bridges and generalizes parasitic source of \gls{sr} and reflecting element of \gls{ris} via smart input design.
	% ! An application scenario was considered where multiple Metascatters ride over a point-to-point transmission to simultaneously encode self message and perform passive beamforming.
	% To fully accommodate backscatter characteristics, we also propose a novel receiving strategy that first jointly decodes all Metascatter from accumulated energy, then models their reflection pattern and backscatter paths within equivalent channel for primary decoding.
	% minor modifications on existing receivers, easy to perform, fits backscatter characteristics.
	% The contributions of this paper is summarized as follows.

	% ! Φ(c[n]) vs P
	\emph{First,} Metascatter adapts the input probability distribution of a finite-state passive backscatter device based on primary and (cascaded) backscatter \gls{csi} to unify and generalize parasitic source of \gls{sr} and reflecting elements of \gls{ris}.
	The reflection pattern over time is no longer fully random or deterministic, but can be flexibly distributed to balance backscatter encoding and passive beamforming.
	For single-user scenario, when primary link is absolutely prioritized, the distribution falls on one state and Metascatter boils down to conventional \gls{ris}.
	When only considering backscatter performance, the distribution involves the highest entropy and Metascatter is essentially an \gls{ambc} node.

	\emph{Second,} we consider an application scenario where multiple Metascatters ride over a point-to-point transmission, exploiting additional propagation paths to simultaneously transmit and assist.
	To fully accommodate backscatter characteristics, we also propose a novel receiving strategy that first jointly decodes all Metascatter from accumulated energy, then models their reflection pattern and backscatter paths within equivalent channel for primary decoding.
	Since backscatter message is modulated over primary signal, backscatter decoding is indeed part of primary channel training, and there is no need for operation-intensive \gls{sic} at the receiver.

	% \emph{Second,} we propose a novel receiving strategy where the backscatter symbol of all tags are first recovered by energy-based decoding, then modeled within equivalent \gls{csi} for primary decoding.
	% When the ratio of backscatter symbol period over primary symbol period is large enough, the randomness of primary source can be averaged out and the performance of non-coherent backscatter decoding can be greatly improved.
	% Since the primary and backscatter symbols are mixed by multiplication coding, the backscatter decoding can be viewed as part of primary channel training, which avoids non-coherent encoding at the transmitter and \gls{sic} at the receiver.

	\emph{Third,} we evaluate the achievable primary-(total-)backscatter rate region by optimizing the input distribution at Metascatters, the active beamforming at the \gls{ap}, and the decision regions at the user. Since the original problem is highly non-convex, we consider a suboptimal \gls{bcd} algorithm where the \gls{kkt} input distribution is numerically evaluated by limit of sequences, the active beamforming is iteratively updated by \gls{pgd} accelerated by backtracking line search, and the decision regions are first restricted to convex, then refined by existing thresholding designs.

	% \emph{Third,} we characterize the achievable primary-(total-)backscatter rate region by iteratively optimizing the tag input distribution, the backscatter decision threshold, and the transmit precoder.
	% For the input design, we propose a numerical method to evaluate the \gls{kkt} solutions by limits of sequences.
	% For the threshold design, we derive the minimum number of decision thresholds to maximize the total backscatter rate, and obtain the optimal thresholds by \gls{dp} accelerated by \gls{smawk} algorithm.
	% However, the optimal precoder design can be non-trivial and we may end up with a low-complexity suboptimal solution.

@@

\begin{section}{Backscatter Principles}
	% \begin{figure}[!t]
	% 	\centering
	% 	\subfloat[Block Diagram]{
	% 		\resizebox{0.8\columnwidth}{!}{
	% 			\input{assets/illustration/block_diagram.tex}
	% 		}
	% 		\label{fi:block_diagram}
	% 	}
	% 	\\
	% 	\subfloat[Equivalent Circuit]{
	% 		\resizebox{0.95\columnwidth}{!}{
	% 			\input{assets/illustration/equivalent_circuit.tex}
	% 		}
	% 		\label{fi:equivalent_circuit}
	% 	}
	% 	\\
	% 	\subfloat[Scatter Model]{
	% 		\resizebox{0.8\columnwidth}{!}{
	% 			\input{assets/illustration/scatter_model.tex}
	% 		}
	% 		\label{fi:scatter_model}
	% 	}
	% 	\caption{Block diagram, equivalent circuit, and scatter model of a typical passive tag. The solid and dashed vectors represent signal and energy flows. The backscatter antenna behaves as a constant power source, where the voltage $V_0$ and current $I_0$ are introduced by incident electric field $\vec{E}_{\mathrm{I}}$ and magnetic field $\vec{H}_{\mathrm{I}}$ \cite{Huang2021}.}
	% \end{figure}

	\begin{figure*}[!t]
		\centering
		\subfloat[Block Diagram]{
			\resizebox{0.32\linewidth}{!}{
				\input{assets/illustration/block_diagram.tex}
			}
			\label{fi:block_diagram}
		}
		\subfloat[Equivalent Circuit]{
			\resizebox{0.37\linewidth}{!}{
				\input{assets/illustration/equivalent_circuit.tex}
			}
			\label{fi:equivalent_circuit}
		}
		\subfloat[Scatter Model]{
			\resizebox{0.28\linewidth}{!}{
				\input{assets/illustration/scatter_model.tex}
			}
			\label{fi:scatter_model}
		}
		\caption{Block diagram, equivalent circuit, and scatter model of a passive backscatter node. The solid and dashed vectors represent signal and energy flows. The backscatter antenna behaves as a constant power source, where the voltage $V_0$ and current $I_0$ are introduced by incident electric field $\vec{E}_{\mathrm{I}}$ and magnetic field $\vec{H}_{\mathrm{I}}$ \cite{Huang2021}.}
	\end{figure*}

@@

	\begin{subsection}{SR: Backscatter Modulation}
		% Backscatter sources encode self message by \emph{randomly changing reflection states.} For $M$-ary \gls{qam}, reflection coefficient $\Gamma_m$ maps to the corresponding complex constellation point $c_m$ by \cite{Thomas2012a}
		Backscatter sources encode self message by \emph{random reflection states variation.} For $M$-ary \gls{qam}, reflection coefficient $\Gamma_m$ maps to the corresponding \emph{complex constellation point $c_m$} by \cite{Thomas2012a}
		\begin{equation}
			\Gamma_m = \alpha \frac{c_m}{\max_{m'} \lvert c_{m'} \rvert},
			\label{eq:backscatter_modulation}
		\end{equation}
		where $0 \le \alpha \le 1$ is the amplitude reflect ratio that controls the harvest-scatter tradeoff at the direction of interest.
		% When the \gls{csi} and reflection alphabet $\{\Gamma_1,\ldots,\Gamma_M\}$ are available at the reader, it can decode the tag message from the observed scattered signal.
		% ! Use larger alpha in simulation: for high-order QAM, some constellation point may harvests more power than others

@@

	\begin{subsection}{IRS: Channel Reconfiguration}
		% \gls{ris} elements assist legacy transmission by \emph{deterministically choosing phase shifts} based on relevant \gls{csi}. For a reflecting element with $M$ candidate states, reflection coefficient $\Gamma_m$ maps to the corresponding phase shift $\theta_m$ by \cite{Wu2018}
		\gls{ris} elements assist legacy transmission by \emph{deterministic phase shifts selection} based on relevant \gls{csi}.
		For a reflecting element with $M$ candidate states, reflection coefficient $\Gamma_m$ relates to the corresponding \emph{phase shift $\theta_m$} by \cite{Wu2018}
		\begin{equation}
			\Gamma_m = \beta_m \exp(j \theta_m),
		\end{equation}
		where $0 \le \beta_m \le 1$ is overall amplitude reflect ratio of state $m$.
		% Based on relevant \gls{csi}
	\end{subsection}
	% Tags periodically switch between different states to perform backscatter modulation.
	% For $M$-ary \gls{qam}, the complex constellation point $c_m \in \mathcal{C}$ maps to the reflection coefficient by \cite{Thomas2012a}
	% \begin{equation}
	% 	\Gamma_m = \alpha \frac{c_m}{\max_{m'} \lvert c_{m'} \rvert},
	% 	\label{eq:backscatter_modulation}
	% \end{equation}
	% where $\alpha \in [0,1]$ models the harvest-backscatter ratio at the direction of interest.
	% For passive tags, $\alpha \ll 1$ is commonly assumed as the majority of the incident wave can be harvested to support tag modules \cite{Thomas2012a}.

	\begin{subsection}{Metascatter: Bridge and Generalization}

@@

				Input probability distribution and time block structure of \gls{sr}, \gls{ris}, and Metascatter.

@@

				Within channel coherence time, Metascatter semi-randomly selects reflection state for each backscatter block, with guidance from input probability distribution.

@@

			\label{fi:metascatter}

@@

		Metascatters simultaneously transmit and assist by \emph{adaptive input distribution design} based on primary and (cascaded) backscatter \gls{csi}.

@@

		% Instead of using fully random or deterministic reflection pattern over time, as shown in Fig. \ref{fi:metascatter}, Metascatter flexibly controls input distribution of candidate reflection states to balance backscatter encoding and passive beamforming.
		% Instead of using fully random or deterministic reflection pattern over time, as shown in Fig. \ref{fi:metascatter}, Metascatter semi-randomly selects reflection state for each backscatter block with guidance from \emph{input probability distribution $P(\Gamma_m)$.}
		% Instead of using fully random or deterministic reflection pattern over time, as shown in Fig. \ref{fi:metascatter}, Metascatter semi-randomly selects reflection state for each backscatter block, with guidance from \emph{input probability distribution $P(\Gamma_m)$.} In other words, it flexibly controls input distribution of candidate reflection states to balance backscatter encoding and passive beamforming. \gls{sr} and \gls{ris} can be regarded as extreme cases of Metascatter, where node input distribution boils down to uniform and deterministically biased, respectively.

>>>>

% dark mode
% \usepackage{xcolor} \pagecolor[rgb]{0,0,0} \color[rgb]{1,1,1}

@@

% glossaries-extra
\setabbreviationstyle[acronym]{long-short}
\newacronym{af}{AF}{Amplify-and-Forward}
\newacronym{ambc}{AmBC}{Ambient Backscatter Communications}
\newacronym{ap}{AP}{Access Point}
\newacronym{awgn}{AWGN}{Additive White Gaussian Noise}
\newacronym{bcd}{BCD}{Block Coordinate Descent}
\newacronym{bc}{BackCom}{Backscatter Communications}
\newacronym{bibo}{BIBO}{Binary-Input Binary-Output}
\newacronym{bpcu}{\si{bpcu}}{bits per channel use}
\newacronym{bpsphz}{\si{bps/Hz}}{bits per second per Hertz}
\newacronym{cp}{CP}{Canonical Polyadic}
\newacronym{cr}{CR}{Cognitive Radio}
\newacronym{cscg}{CSCG}{Circularly Symmetric Complex Gaussian}
\newacronym{csi}{CSI}{Channel State Information}
\newacronym{df}{DF}{Decode-and-Forward}
\newacronym{dmc}{DMC}{Discrete Memoryless Channel}
\newacronym{dmtc}{DMTC}{Discrete Memoryless Thresholding Channel}
\newacronym{dmtmac}{DMTMAC}{Discrete Memoryless Thresholding Multiple Access Channel}
\newacronym{dtmac}{DTMAC}{Discrete Thresholding Multiple Access Channel}
\newacronym{dp}{DP}{Dynamic Programming}
\newacronym{fdma}{FDMA}{Frequency-Division Multiple Access}
\newacronym{iid}{i.i.d.}{independent and identically distributed}
\newacronym{ioe}{IoE}{Internet of Everything}
\newacronym{iot}{IoT}{Internet of Things}
\newacronym{kkt}{KKT}{Karush-Kuhn-Tucker}
\newacronym{m2m}{M2M}{Machine to Machine}
\newacronym{mac}{MAC}{Multiple Access Channel}
\newacronym{mc}{MC}{Multiplication Coding}
\newacronym{miso}{MISO}{Multiple-Input Single-Output}
\newacronym{mimo}{MIMO}{Multiple-Input Multiple-Output}
\newacronym{ml}{ML}{Maximum-Likelihood}
\newacronym{mrt}{MRT}{Maximum Ratio Transmission}
\newacronym{noma}{NOMA}{Non-Orthogonal Multiple Access}
\newacronym{ofdm}{OFDM}{Orthogonal Frequency-Division Multiplexing}
\newacronym{pdf}{PDF}{Probability Density Function}
\newacronym{pgd}{PGD}{Projected Gradient Descent}
\newacronym{psk}{PSK}{Phase Shift Keying}
\newacronym{qam}{QAM}{Quadrature Amplitude Modulation}
\newacronym{qos}{QoS}{Quality of Service}
\newacronym{rf}{RF}{Radio-Frequency}
\newacronym{rfid}{RFID}{Radio-Frequency Identification}
\newacronym{ris}{RIS}{Reconfigurable Intelligent Surface}
\newacronym{sc}{SC}{Superposition Coding}
\newacronym{sic}{SIC}{Successive Interference Cancellation}
\newacronym{simo}{SIMO}{Single-Input Multiple-Output}
\newacronym{sinr}{SINR}{Signal-to-Interference-plus-Noise Ratio}
\newacronym{smawk}{SMAWK}{Shor-Moran-Aggarwal-Wilber-Klawe}
\newacronym{snr}{SNR}{Signal-to-Noise Ratio}
\newacronym{sr}{SR}{Symbiotic Radio}
\newacronym{tdma}{TDMA}{Time-Division Multiple Access}
\newacronym{ue}{UE}{user}
\newacronym{wit}{WIT}{Wireless Information Transfer}
\newacronym{wpcn}{WPCN}{Wireless Powered Communication Network}
\newacronym{wpt}{WPT}{Wireless Power Transfer}

\begin{document}
\title{UniScatter: Unifying\\Backscatter Communications, Symbiotic Radio and Reconfigurable Intelligent Surface}
\author{
	\IEEEauthorblockN{
		Yang~Zhao,~\IEEEmembership{Member,~IEEE,}
		and~Bruno~Clerckx,~\IEEEmembership{Fellow,~IEEE}
	}
	\thanks{
		The authors are with the Department of Electrical and Electronic Engineering, Imperial College London, London SW7 2AZ, U.K. (e-mail: \{yang.zhao18, b.clerckx\}@imperial.ac.uk).
	}
}
\maketitle

\begin{abstract}
	Scatterers can harvest energy from, modulate information over, and influence propagation of surrounding radio waves.
	\gls{bc} varies object impedance to manipulate the magnitude, phase, and/or frequency of scattered signal to encode information and deliver within coverage.
	\gls{ris} adapts scattering antennas or programmable metamaterial to control wireless propagation environment by boosting/suppressing signal strength in specific directions.
	\gls{sr} incorporates scatter nodes into active networks that recycle ambient signal to transmit self information and enhance legacy channel to the cooperative receiver.
	In this paper, we depart from those concepts and introduce UniScatter as a new paradigm for future wireless networks.
	Instead of treating probability distribution of reflection states as equiprobable (as scattering source of \gls{bc}/\gls{sr}) or degenerate (as reflecting element of \gls{ris}), UniScatter node adapts the input distribution of a passive scatterer based on link priority and \gls{csi}, balancing information encoding and channel reconfiguration in a flexible and mutualistic manner.
	To accommodate signal characteristics, UniScatter receiver semi-coherently decodes all nodes from accumulated energy, determines equivalent primary channel over reflection pattern, then coherently decodes the primary link under enhanced multipath.
	It reduces the complexity of cooperative decoding while preserves the benefits of backscatter modulation and passive beamforming.
	Using shared spectrum, energy, and infrastructures, UniScatter is a general and powerful transmit-assist protocol that unifies \gls{bc}, \gls{ris} and \gls{sr} with universal hardware design and augmented \gls{qos} control.
	We consider an application scenario where a multi-antenna \gls{ap} serves a single-antenna user surrounded by multiple UniScatter nodes, and characterize the achievable primary-total-backscatter rate region by designing input distribution at the nodes, active beamforming at the \gls{ap}, and backscatter decision regions at the user.
	Simulation results demonstrate UniScatter nodes can flexibly control the transmit-assist tradeoff via smart input distribution design.
\end{abstract}

@@

	To the best of our knowledge, all relevant literatures assumed either Gaussian codebook \cite{Guo2019b,Ding2020,Long2020a,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Hu2021b} or finite equiprobable inputs \cite{Yang2018,Liang2020,Han2021,Zhang2022,Liu2019d,Bereyhi2020,Xu2020b,Zhang2021d,Hua2022,Basar2020,Ma2020a,Yuan2021,Hu2021a} at backscatter information sources.
	The former is impractical for passive backscatter devices, while the latter does not fully exploit reflection pattern and \gls{csi}.
	In this paper, we introduce UniScatter that generalizes \gls{bc}, \gls{sr}, and \gls{ris} to manipulate the transmit-assist tradeoff via smart input distribution and backscatter detector design.
	The contributions of this paper are summarized as follows.

	\emph{First,} we propose UniScatter node to adapt the input probability distribution of a finite-state passive scatter device based on link priority and \gls{csi}.
	The reflection pattern over time is no longer fully random or deterministic, but can be flexibly distributed to unify and balance backscatter modulation with passive beamforming.
	Scattering source of \gls{bc}/\gls{sr} and reflecting element of \gls{ris} can be regarded as its extreme cases, where the input distribution boils down to equiprobable and degenerate, respectively.
	Like aforementioned \gls{ris}-empowered \gls{bc}/\gls{sr} schemes, the passive nodes require regular coordination with active devices, but the advantages are 1) UniScatter nodes can be built over conventional load-switching scatterers instead of composite metamaterial; 2) the optimization cost of input distribution is much lower than that of \gls{ris} reflection coefficients; 3) adaptive channel coding at backscatter sources can exploit \gls{csi} to achieve higher instantaneous rate than conventional uncoded transmission.

	\emph{Second,} we propose a practical receiving strategy that semi-coherently decodes all UniScatter messages from the received energy during each backscatter symbol block, re-encodes and recovers their reflection patterns at each primary block, combines those with relevant \gls{csi} to construct equivalent primary channels, then coherently decodes the primary link under adapted multipath.
	The proposed receiver 1) preserves the benefits of backscatter modulation and passive beamforming; 2) enjoys lower computational and operational complexities than joint \gls{ml} and \gls{sic} schemes; 3) accommodates the difference of symbol period in backscatter decoding; 4) exploits the reflection patterns in primary decoding; 5) suits for diverse symbol period ratios.

	\emph{Third,} we consider an application scenario where multiple UniScatter nodes ride over a point-to-point \gls{miso} transmission, performing backscatter modulation and passive beamforming to a nearby user using shared spectrum, energy, and infrastructures.
	To investigate how UniScatter unifies \gls{bc}, \gls{sr} and \gls{ris} for the benefits of both coexisting subsystems, we provide primary and backscatter rate analyses and emphasize the contributions of input distribution at UniScatter nodes, active beamforming at the \gls{ap}, and backscatter decision regions at the user.
	This is the first paper to reveal the importance of those factors in \gls{ris}-empowered \gls{bc}/\gls{sr}.

	\emph{Fourth,} we characterize the achievable primary-total-backscatter rate region of the aforementioned system by optimizing the input distribution, active beamforming, and backscatter decision regions.
	It is formulated as a weighted sum-rate maximization subject to input probability simplex, average transmit power, and sequential decision threshold constraints.
	Since the original problem is highly non-convex, we decouple it into individual subproblems and constraint all decision regions to convex (connected) intervals.
	A suboptimal \gls{bcd} algorithm is then proposed, where the \gls{kkt} input distribution is numerically evaluated by limit of sequences, the active beamforming is iteratively updated by \gls{pgd} accelerated by backtracking line search, and the decision regions are refined by existing thresholding designs.

	\emph{Fifth,} we provide numerical results to demonstrate the benefits of UniScatter and proposed algorithms.
	It is concluded that 1) UniScatter nodes provide flexible transmit-assist tradeoff using adaptive input distribution design; 2) when primary link is absolutely prioritized, the input probability of each node is \num{1} at one state and \num{0} at the others, which coincides with discretized \gls{ris}; 3) when backscatter link is absolutely prioritized, UniScatter nodes can exploit adaptive channel coding to achieve higher instantaneous rate than uncoded equiprobable transmission of \gls{bc}/\gls{sr}; 4) the proposed \gls{kkt} input distribution design converges to stationary points, whose average performance is very close to global optimal; 5) the \gls{pgd} beamforming achieves larger rate region than conventional \gls{mrt}; 6) the decision region schemes adapted to input distribution provide higher backscatter rates than the non-adaptive \gls{ml} detector; 7) cooperation between passive nodes in terms of joint encoding can further boost the total backscatter rate; 8) the low complexity of input distribution design and the marginal effect of increasing reflection states motivates the use of low-order scatter nodes to replace high-resolution \gls{ris}.

@@

\begin{section}{Backscatter Principles}
	\begin{figure*}[!t]
		\centering
		\subfloat[Block Diagram]{
			\resizebox{0.32\linewidth}{!}{
				\input{assets/illustration/block_diagram.tex}
			}
			\label{fi:block_diagram}
		}
		\subfloat[Equivalent Circuit]{
			\resizebox{0.37\linewidth}{!}{
				\input{assets/illustration/equivalent_circuit.tex}
			}
			\label{fi:equivalent_circuit}
		}
		\subfloat[Scatter Model]{
			\resizebox{0.28\linewidth}{!}{
				\input{assets/illustration/scatter_model.tex}
			}
			\label{fi:scatter_model}
		}
		\caption{Block diagram, equivalent circuit, and scatter model of a passive backscatter node. The solid and dashed vectors represent signal and energy flows. The backscatter antenna behaves as a constant power source, where the voltage $V_0$ and current $I_0$ are introduced by incident electric field $\vec{E}_{\mathrm{I}}$ and magnetic field $\vec{H}_{\mathrm{I}}$ \cite{Huang2021}.}
	\end{figure*}

@@

	\begin{subsection}{BackCom/SR: Backscatter Modulation}
		% Backscatter sources encode self message by \emph{randomly changing reflection states.} For $M$-ary \gls{qam}, reflection coefficient $\Gamma_m$ maps to the corresponding complex constellation point $c_m$ by \cite{Thomas2012a}
		Backscatter sources encode self message by \emph{random reflection states variation.} For $M$-ary \gls{qam}, reflection coefficient $\Gamma_m$ maps to the corresponding \emph{complex constellation point $c_m$} by \cite{Thomas2012a}
		\begin{equation}
			\Gamma_m = \alpha \frac{c_m}{\max_{m'} \lvert c_{m'} \rvert},
			\label{eq:backscatter_modulation}
		\end{equation}
		where $0 \le \alpha \le 1$ is the amplitude reflect ratio that controls the harvest-scatter tradeoff at the direction of interest.
		% When the \gls{csi} and reflection alphabet $\{\Gamma_1,\ldots,\Gamma_M\}$ are available at the reader, it can decode the tag message from the observed scattered signal.
		% ! Use larger alpha in simulation: for high-order QAM, some constellation point may harvests more power than others

@@

	\begin{subsection}{RIS: Channel Reconfiguration}
		% \gls{ris} elements assist legacy transmission by \emph{deterministically choosing phase shifts} based on relevant \gls{csi}. For a reflecting element with $M$ candidate states, reflection coefficient $\Gamma_m$ maps to the corresponding phase shift $\theta_m$ by \cite{Wu2018}
		\gls{ris} elements assist legacy transmission by \emph{deterministic phase shifts selection} based on relevant \gls{csi}.
		For a reflecting element with $M$ candidate states, reflection coefficient $\Gamma_m$ relates to the corresponding \emph{phase shift $\theta_m$} by \cite{Wu2018}
		\begin{equation}
			\Gamma_m = \beta_m \exp(j \theta_m),
		\end{equation}
		where $0 \le \beta_m \le 1$ is overall amplitude reflect ratio of state $m$.
		% Based on relevant \gls{csi}
	\end{subsection}
	% Tags periodically switch between different states to perform backscatter modulation.
	% For $M$-ary \gls{qam}, the complex constellation point $c_m \in \mathcal{C}$ maps to the reflection coefficient by \cite{Thomas2012a}
	% \begin{equation}
	% 	\Gamma_m = \alpha \frac{c_m}{\max_{m'} \lvert c_{m'} \rvert},
	% 	\label{eq:backscatter_modulation}
	% \end{equation}
	% where $\alpha \in [0,1]$ models the harvest-backscatter ratio at the direction of interest.
	% For passive tags, $\alpha \ll 1$ is commonly assumed as the majority of the incident wave can be harvested to support tag modules \cite{Thomas2012a}.

	\begin{subsection}{UniScatter: Bridge and Generalization}

@@

				Input probability distribution and time block structure of \gls{sr}, \gls{ris}, and UniScatter.

@@

				Within channel coherence time, UniScatter nodes semi-randomly select reflection state for each backscatter block, with guidance from input probability distribution.

@@

			\label{fi:uniscatter}

@@

		UniScatter nodes simultaneously transmit and assist by \emph{adaptive input distribution design} based on primary and (cascaded) backscatter \gls{csi}.

@@

		% Instead of using fully random or deterministic reflection pattern over time, as shown in Fig. \ref{fi:uniscatter}, UniScatter flexibly controls input distribution of candidate reflection states to balance backscatter encoding and passive beamforming.
		% Instead of using fully random or deterministic reflection pattern over time, as shown in Fig. \ref{fi:uniscatter}, UniScatter semi-randomly selects reflection state for each backscatter block with guidance from \emph{input probability distribution $P(\Gamma_m)$.}
		% Instead of using fully random or deterministic reflection pattern over time, as shown in Fig. \ref{fi:uniscatter}, UniScatter semi-randomly selects reflection state for each backscatter block, with guidance from \emph{input probability distribution $P(\Gamma_m)$.} In other words, it flexibly controls input distribution of candidate reflection states to balance backscatter encoding and passive beamforming. \gls{sr} and \gls{ris} can be regarded as extreme cases of UniScatter, where node input distribution boils down to uniform and deterministically biased, respectively.
		Instead of using fully random or deterministic reflection pattern over time, as shown in Fig. \ref{fi:uniscatter}, UniScatter nodes semi-randomly select reflection state for each backscatter block, with \emph{guidance of input probability $P(\Gamma_m)$} for state $m$. In other words, it flexibly controls input distribution of candidate reflection states to balance backscatter encoding and passive beamforming.
		% \gls{sr} and \gls{ris} can be regarded as extreme cases of UniScatter nodes, where node input distribution boils down to uniform and deterministic, respectively.
